\thesistitle

### 2019-08-25 sections/experimentalsetup.tex
Experimental Setup

\subsection{Filtering Maven projects}
As explained in Section~\ref{chap:challenge}, CloneRefactor requires all the libraries a software project is dependent on to perform its clone analysis. As these are not included in the corpus by Allamanis \cite{githubCorpus2013}, we created a script to gather these dependencies. As Java projects manage their dependencies in many different ways, we decided to limit our scope to a single build automation system. We chose Maven, as it is one of the most used build automation systems for Java projects. Maven uses a file, named \texttt{pom.xml}, to describe a projects' dependencies. Our script clones the latest version of each project in the corpus. It then removes each project that has no \texttt{pom.xml} file (which indicates that those do not use the Maven build automation system).

We then continued to filter all test cases and generated files. As many projects store these files in many different places, we decided to further filter the corpus to only include projects with a conventional structure. For Maven, projects are recommended to put their production code in the folder structure \texttt{src/main/java}. We omitted Maven projects that do not adhere to this convention. We instruct CloneRefactor only to use the sources in the \texttt{src/main/java} folder. This decreases the chance of generated files and test code being considered for clone detection.

@@

\subsection{Resulting corpus}
This procedure results in 2,267 Java projects including all their dependencies. The projects vary in size and quality. The total size of all projects is 14.210.357 lines (11,315,484 when excluding whitespace) over a total of 99,586 Java files. This is an average of 6,268 lines over an average of 44 files per project, 141 lines on average per file. The largest project in the corpus is \textit{VisAD} with 502,052 lines over 1,527 files.

@@

We also test the correctness of the resulting code after refactoring. For this, we use a GitHub project named JFreeChart. JFreeChart has high test coverage and working tests, which allows us to test the correctness of the program after running CloneRefactor. We run CloneRefactor manually over the JFreeChart project, run its test cases and check the correctness of the proposed refactorings.

\section{Minimum clone size}
In this study, we want to find out what thresholds will improve maintainability if clones by those thresholds are refactored. For example, when clones are very small, refactoring them might not improve maintainability since the detrimental effect of the added volume of the newly created method exceeds the positive effect of removing duplication. Because of that, we perform all our experiments with a minimum clone size of 10 tokens, because smaller clones cannot improve maintainability when refactored.

The reason for this is that when applying the ``Extract Method'' refactoring technique, we create a new method. An empty method in Java consists of 7 tokens. We also need calls to the extracted method, which is 4 tokens per call if no arguments are required. Empirically, we found all clones below 10 tokens in size, are very unlikely to affect maintainability positively. To avoid such clones polluting our data, we do not consider clones smaller than 10 tokens.

>>>>

\subsection{Filtering Maven projects}
As explained in Section~\ref{chap:challenge}, CloneRefactor requires all the libraries a software project is dependent on to perform its clone analysis. As these are not included in the corpus by Allamanis \cite{githubCorpus2013}, we created a script to gather these dependencies. As Java projects manage their dependencies in many different ways, we decided to limit our scope to a single build automation system. We chose Maven, as it is one of the most used build automation systems for Java projects. Maven uses a file, named \texttt{pom.xml}, to describe a projects' dependencies. Our script clones the latest version of each project in the corpus. It then removes each project that has no \texttt{pom.xml} file (which indicates that those projects do not use the Maven build automation system).

We then continued to filter all test code and generated files. As many projects store these files in many different places, we decided to further filter the corpus to only include projects with a conventional structure. When using Maven, projects are recommended to put their production code in the folder structure \texttt{src/main/java}. We omitted Maven projects that do not adhere to this convention. We instruct CloneRefactor only to use the sources in the \texttt{src/main/java} folder. This decreases the chance of generated files and test code being considered for clone detection.

@@

\subsection{Resulting corpus}
This procedure results in 2,267 Java projects including all their dependencies\footnote{The full list of projects is in the following file in our GitHub repository: \url{https://github.com/SimonBaars/GitHub-Java-Corpus-Scripts/blob/master/filtered_projects.txt}}. The projects vary in size and quality. The total size of all projects is 14.210.357 lines (11,315,484 when excluding whitespace) over a total of 99,586 Java files. This is an average of 6,268 lines over an average of 44 files per project, 141 lines on average per file. The largest project in the corpus is \textit{VisAD} with 502,052 lines over 1,527 files.

@@

We also test the correctness of the resulting code after refactoring. For this, we use a project named JFreeChart\footnote{JFreeChart is available on GitHub: \url{https://github.com/jfree/jfreechart}}. JFreeChart has high test coverage and working tests, which allows us to test the correctness of the program after running CloneRefactor. We run CloneRefactor manually over the JFreeChart project, run its test cases and check the correctness of the proposed refactorings.

\section{Minimum clone size}
In this study, we want to find out what thresholds will improve maintainability if clones by those thresholds are refactored. For example, when clones are very small, refactoring them might not improve maintainability since the detrimental effect of the added volume of the newly created method exceeds the positive effect of removing duplication. Because of that, we perform all our experiments with a minimum clone size of 10 tokens, because smaller clones almost never improve maintainability when refactored.

The reason for this is that when applying the ``Extract Method'' refactoring technique, we create a new method. An empty method in Java consists of 7 tokens. We also need calls to the extracted method, which is 4 tokens per call if no parameters/arguments are required. Empirically, we found all clones below 10 tokens in size, are very unlikely to affect maintainability positively. To avoid such clones polluting our data, we do not consider clones smaller than 10 tokens.
